\documentclass{ethan_cv}

\setname{Ethan Cavill}{}
\setmobile{+1 858 518-4580}
\setmail{ethancavill@gmail.com}
\setlinkedinaccount{https://www.linkedin.com/in/ethancavill}
\setgithubaccount{https://github.com/earcherc}
\setportfolioaccount{https://ethancavill.me}
\setthemecolor{MidnightBlue}
\setcitizenship{U.S. Citizen}

\begin{document}

% Create header
\headerview
\vspace{1ex} % white space

\section{Experience}
    \datedexperience{Adelaide MRI}{Aug 2020 - Oct 2023}
    \explanation{Full Stack Software Engineer}{Adelaide, SA}
    \explanationdetail{
        \smallskip
        \coloredbullet\ %
        Developed patented radiology reporting software with Angular, Flask, and ML models; boosting output by \textbf{2-4x}.
        
        \coloredbullet\ %
        Transitioned legacy invoicing to automated software solution with MediPass payment API and webhook integration.

        \coloredbullet\ %
        Wrote integration and unit tests with PyTest (\textbf{90\%+ coverage}) and end-to-end tests with Cypress.

        \coloredbullet\ %
        Led development of patient booking system using React, GCP, and FastAPI, alleviating call burden \textbf{by 50\%}.
        
        \coloredbullet\ %
        Managed large codebase version upgrades, requiring careful refactoring of business critical components.

        \coloredbullet\ %
        Led frontend migration of rostering software from React to Angular, improving maintainability.     
        
        \coloredbullet\ %
        Implemented strict linting, compiler settings and other tooling to improve DX and reduce sentry errors \textbf{by 30\%}.

        \coloredbullet\ %
        Aided in engineering interviews, evaluating candidate's technical skills and cultural fit.
        \smallskip
    }
    %
    \datedexperience{Tangible AI}{Oct 2023 - Jan 2024} 
    \explanation{Machine Learning Engineer}{San Diego, CA} 
    \explanationdetail{ 
        \smallskip 
        \coloredbullet\ %
        Developed and evaluated a PyTorch seq-to-seq neural network translator for language translation.
        
        \coloredbullet\ %
        Reduced bugs and improved user experience in Django built LLM chat-bot management software.

        \coloredbullet\ %
        Built an open-source vector space (BERT) search engine to improve corpus searchability, resulting in an \textbf{88\% improvement} in recall over TF-IDF. Forked to create 'Knowt', an open-source RAG project.

        \coloredbullet\ %
        Presented findings on information retrieval systems to \textbf{30+ attendees} at a Python User Group, with \textbf{\href{https://www.ethancavill.me/blog/information-retrieval-systems}{blog}}.

        \coloredbullet\ %
        Proofread and published edits to 'Natural Language Processing in Action', improving clarity in \textbf{10 chapters}.
        \smallskip
    }     
    %
    \datedexperience{Clai Studios}{Mar 2024 - Present}
    \explanation{Full Stack Software Engineer}{San Francisco, CA}
    \explanationdetail{
        \smallskip
        \coloredbullet\ %
        Consulted on key architectural and design decisions for a startup improving pain-management outcomes for clients.
        
        \coloredbullet\ %
        Implemented automations to web scrape and schedule social media posting using Python, GCP, and Selenium, \textbf{increasing output by 3x}.

        \coloredbullet\ %
        Consulted with the founder of a health-ed startup on software architecture, feature development, and talent acquisition strategies.
    }
    \vspace{+3mm}

\section{Projects}
    \datedexperience{deepworktimer.io \textnormal{\cpshalf {Next.js, FastAPI, SQLAlchemy, PostgreSQL, Redis, Docker, Ubuntu, AWS}}}{}
    \explanationdetail{
        \smallskip
        \coloredbullet\ %
        Developed a streak-based productivity system that improves focus and engagement on cognitively demanding tasks.

        \coloredbullet\ %
        Integrated authentication and authorization with Redis and PostgreSQL for fast and secure session management.

        \coloredbullet\ %
        Implemented \textbf{containerized} environment with Docker, improving deployment and developer onboarding time.

        \coloredbullet\ %
        Designed a distributed microservice architecture with RabbitMQ, Celery to enhance scalability and fault tolerance.

        \coloredbullet\ %
        Mentored a CS student on contributing to open source, providing hands-on experience in full-stack development.
    \smallskip 
    }
    %
    \datedexperience{devarity.com \textnormal{\cpshalf {PHP, MySQL, Bootstrap, JQuery}}}{}
    \explanationdetail{
        \smallskip
        \coloredbullet\ %
        Developed an indie game platform to provide developers with fair profit margins, launching with over \textbf{50 titles}.
        
        \coloredbullet\ %
        Spearheaded distributor acquisition efforts, securing partnerships with \textbf{four} indie publishing studios.

        \coloredbullet\ %
        Led strategic decision-making across design, marketing, product management, engineering, and launch operations.

        \coloredbullet\ %
        Coordinated outsourcing of design and engineering efforts to aid in timely and seamless launch.
    \smallskip 
    }
    %
    \datedexperience{ethancavill.me {\textnormal{\cpshalf {Next.js, Tailwind CSS, Framer Motion, MDX, Vercel}}}}{}
    \explanationdetail{
        \smallskip
        \coloredbullet\ %
        Developed a portfolio website with React and Markdown to showcase projects, services, and written insights.
    }
    %

    \section{Skills}
        \small
        \begin{tabular}{p{2.25cm} p{16cm}}
            \textbf{Languages} & Python, JavaScript, TypeScript, Golang (Go), Java, SQL, HTML/CSS, Bash \\ 
            \addlinespace[1.5mm]
            \textbf{Technologies} & React, Angular, Redux, Zustand, Jotai, RxJS, Docker, Kubernetes, Linux, Flask, FastAPI, Django, PostgreSQL, MongoDB, Redis, Celery, RabbitMQ, PyTorch, PyTest, Cypress, Sentry, Selenium, Grafana, GCP, AWS \\
            \addlinespace[1.5mm]
            \textbf{Concepts} & Full-Stack Development, Frontend Development, Backend Development, OOP, Functional Programming, Systems Design, Reactive Programming, State Management, Technical Writing, Agile, Scrum, Algorithms and Data Structures, Machine Learning, Data Science, Distributed Systems, REST, GraphQL, Integration Testing, Unit Testing, End-to-End Testing, Version Control, Git, CI/CD, DevOps, Observability
        \end{tabular}
    \vspace{+3mm}


\section{Education}
    \datedexperience{Bachelor of Mathematical Sciences}{Mar 2021 - Nov 2023}
    \explanation{University of Adelaide}{Adelaide, SA} 
    \explanationdetail{
        \smallskip
        \coloredbullet\ Linear algebra and calculus classes foundational to computer science and machine learning. \\
    }
    \datedexperience{Bachelor of Economics and Finance}{Mar 2017 - Nov 2020}
    \explanation{University of Adelaide}{Adelaide, SA} 
    \explanationdetail{
        \smallskip
        \coloredbullet\ Foundations in modern and classical economic theory with financial modelling, statistics and data analytics. \\
        }

\end{document}
