\documentclass{jon-sundin-cv}

\setname{JON SUNDIN}{}
\setmobile{+1 310 741 0244}
\setmail{sundinjon@gmail.com}
\setlinkedinaccount{https://www.linkedin.com/in/jonsundin}
\setgithubaccount{https://github.com/jmsundin}
\setportfolioaccount{https://jonsundin.com}
\setthemecolor{MidnightBlue}
\setcitizenship{U.S. Citizen}

\begin{document}

% Create header
\headerview
\vspace{1ex} % white space

\section{Experience}
    \datedexperience{Revature LLC}{2024}
    \explanation{Software Engineer in Test Automation Engineering}{Remote}
    \explanationdetail{

        \coloredbullet\ %
        Used Java, JUnit, Cucumber, Selenium and web technologies (HTML \& CSS) to write automated tests that \textbf{reduced manual testing time by 90\%}.
        
        \coloredbullet\ %
        Used Jira for project management and Agile behavior-driven test development to document application features and associated test cases.

        \coloredbullet\ %
        Worked in a team of 4 software engineers to create automated systems tests and user acceptance tests with \textbf{90\% code coverage}.
    }
    %
    \datedexperience{Tangible AI}{2023} 
    \explanation{Software Engineer, Frontend}{Remote} 
    \explanationdetail{ 

        \coloredbullet\ %
        Created an open-source graph visualization using D3.js, and vanilla JavaScript to visualize a chatbot conversation flow.

        \coloredbullet\ %
        Added a backend API using Django.

        \coloredbullet\ %
        Collaborated with a team of 3 engineers.

    }     
    %
    \datedexperience{SubThought Corp}{2023}
    \explanation{Software Engineer}{Remote}
    \explanationdetail{

        \coloredbullet\ %
        Technologies used: JavaScript, TypeScript, XML.

        \coloredbullet\ %
        Taught myself TextMate Language Grammar and the VS Code Language Extension API.

        \coloredbullet\ %
        Collaborated with the product owner to create a language extension for a new functional programming language, enabling syntax highlighting in VS Code.

    }     
    %
    \datedexperience{Tangible AI}{2021}
    \explanation{Software Engineer, Intern}{Remote}
    \explanationdetail{

        \coloredbullet\ %
        Learned Python, clustering with K-means (Scikit-Learn), plotting data (Matplotlib and Seaborn).

        \coloredbullet\ %
        Created an interactive visual mapping of noun phrases using word embeddings (spaCy.io)  and dimensionality reduction (T-SNE); github.com/jmsundin/wordmap

    }

    \vspace{+3mm}

\section{Hackathons}
    \datedexperience{Cerebral Beach Gen AI Hackathon}{2024}
    \explanation{1st-Place Prize Winner, Sports \& Media Track}{Santa Monica, CA}
    \explanationdetail{
        \coloredbullet\ %
        Worked in a team of 5 to build a livestream feed and chatbot for sport event video segmentation.

        \coloredbullet\ %
        Frontend Technologies: JavaScript, Next.js, Tailwind CSS; github.com/danielenriquez59/pulselive-frontend.

        \coloredbullet\ %
        Backend Technologies: Python, 12 Labs Video Segmentation API, Llama Index; github.com/danielenriquez59/pulselive-backend.
    }

    \datedexperience{Outer Edge LA Hackathon}{2023}
    \explanation{Bounty Prize Winner}{Santa Monica, CA}
    \explanationdetail{
        \coloredbullet\ %
        Worked with two others to create a web application to interface with a third-party NFT wallet.
    
        \coloredbullet\ %
        Technologies: JavaScript, HTML, CSS, HTTP protocols.
    }

    \datedexperience{AI LA Bioscience Hackathon}{2022}
    \explanation{1st-Place Prize Winner, The All of Us Research Track}{Culver City, CA}
    \explanationdetail{
        \coloredbullet\ %
        Performed exploratory data analysis (EDA) on participant healthcare data to determine correlation between Diabetes Mellitus Type 2 and Long-COVID-19 using a decision tree regression model (Scikit-Learn).
        
        \coloredbullet\ %
        Implemented an interactive tree visualization using D3.js for the regression model.
    
        \coloredbullet\ %
        Collaborated with a cross-functional team of 5 to present preliminary findings in-person at the 2022 AI LA Bioscience Hackathon.
    }

    \vspace{+3mm}

\section{Projects}
    \datedexperience{infoverse.ai \textnormal{\cpshalf {Next.js, D3.js, JavaScript, Tailwind CSS, SPARQL}}}{2022 - 2023}
    \explanationdetail{
        \coloredbullet\ %
        Solo developer on this SPA that provides a graph-based (D3.js) interface for Wikipedia.org (MediaWiki REST endpoint) and Wikidata.org (SPARQL and REST endpoint).
        \coloredbullet\ %
        Solves explorability problem by providing a graph-based interface for Wikipedia.org and Wikidata.org.
    }

\vspace{+3mm}

\section{Education}
    \datedexperience{Master of Science, Software Engineering}{2021 - 2022}
    \explanation{California State University, Fullerton; GPA 3.84}{Fullerton, CA}

    \datedexperience{Doctor of Medicine -- Non-conferred}{2017 - 2020}
    \explanation{Loma Linda University, School of Medicine}{Loma Linda, CA}

    \datedexperience{Bachelor of Science, Biochemistry}{2012 - 2014}
    \explanation{Southern Adventist University; GPA 3.68}{Collegedale, TN}

    \datedexperience{Associate of Science, Pre-Engineering}{2010 - 2013}
    \explanation{Wake Technical Community College; GPA 3.87}{Raleigh, NC}

\end{document}
